Stack Safety is a Security Property

### 2021-04-13 tex/main.tex
Another go at the abstract

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications;
they rely instead on informal descriptions of
the safe stack manipulation behaviors that they allow,
or specific examples of the bad behaviors that they prevent.

We propose a formal criterion \apt{criteria?} for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state''). These properties are sensible even in the presence of
abnormal control flow.\apt{Is this important enough to mention here?}
We further apply\apt{what does this mean? we didn't
  invent it} a straightforward notion of
``well-bracketed control flow'' that restricts control flow to the
typical pattern of matched calls and returns.

We show that our properties describe the behavior of the stack-safety
``micro-policies'' of~\citet{DBLP:conf/sp/RoesslerD18}
using property-based randomized testing. An eager micro-policy
that catches violations immediately enforces our primary ``stepwise''
properties, and we define weaker, more extensional ``observational''
properties that are enforced even by a ``lazy'' micro-policy -- one
that, for performance reasons, may catch violations after they occur
but before they become visible.

We argue \apt{do we?} that our properties are suited to a range of other enforcement
mechanisms. The strict stepwise properties can describe mechanisms
that catch errors immediately, as is typical. While the observational
properties are closely linked to lazy micro-policies they are weak enough
to be a lower bound that captures stack safety for any reasonable enforcement mechanism.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}

  \ifaftersubmission\bcp{should we mention stktokens here?}
  \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  \bcp{Some people say not to, but I think their argument is weak: I've
    added Nick/Andre above.  But I'm not sure we want to get into stkTokens
    in the abstract.}
  \fi
\end{abstract}

@@

%% Keywords
%% comma separated list
\keywords{Stack Safety, Micro-Policies}  %% \keywords are mandatory in final camera-ready submission

>>>>

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
%\apt{maybe: ``Stack safety is a testable security property''?}\bcp{That
%  would sacrifice a lot of oomph for a little bit of precision, IMO.  Prefer
%  to leave it out of the title but hit it strongly in the abstract.}%
What is stack safety? The phrase is associated with a variety of compiler,
run-time, and hardware mechanisms for guarding against corruption of stack
memory.  But these mechanisms typically lack rigorous specifications,
relying instead on informal descriptions of
the safe stack manipulation behaviors that they allow
and/or specific examples of the bad behaviors that they prevent.

We propose formal criteria for stack safety, phrased in terms of
language-based security: a combination of an integrity property (``each
caller's stack frame is held invariant by the callee'') and a confidentiality
property (``the callee's behavior is insensitive to differences in the
caller's state'').
% These properties are sensible even in the presence of
% abnormal control flow.\apt{Is this important enough to mention here?}
% BCP: I think not in the abstract, but maybe in the intro.
% We further apply\apt{what does this mean? we didn't
%  invent it} a straightforward notion of
% ``well-bracketed control flow'' that restricts control flow to the
% typical pattern of matched calls and returns.
%
We argue that these criteria match common intuitions (1) by showing that
they are violated by a variety of intuitively unsafe examples and (2) by
using property-based random testing to check that appropriate variants of
the criteria are actually enforced by the stack-safety ``micro-policies''
proposed by~\citet{DBLP:conf/sp/RoesslerD18}.  Specifically, Roessler and
dehon's ``eager'' micro-policy, which catches violations as early as
possible, enforces simple ``stepwise'' versions of our confidentiality and
integrity properties, while their more performant ``lazy'' micro-policy
enforces weaker, more extensional ``observational'' variants of the
properties.

\bcp{We should mention stack data and coroutines, I think?}

% We argue \apt{do we?}\bcp{I guess we will not have time to.  Propose
%   deleting this para.} that our properties are suited to a range of other
% enforcement mechanisms. The strict stepwise properties can describe
% mechanisms that catch errors immediately, as is typical. While the
% observational properties are closely linked to lazy micro-policies they are
% weak enough to be a lower bound that captures stack safety for any
% reasonable enforcement mechanism.

\apt{This is a good story, but does it describe the paper we are able to produce this week?
  We were rejected before exactly because we claimed to have
  a general criterion, but did not in fact demonstrate its generality (which is not
  obvious). What has changed?}\bcp{I agree with these concerns. Deleted the
  para about the general story.  Does the rest now avoid making (or
  implying) claims that we can't defend?}
\bcp{Also, I think we should save
  WBCF for the intro---I can't find a way to discuss it here that is brief
  and not confusing/distracting.}

  % \ifaftersubmission\bcp{should we mention stktokens here?}
  % \leo{Not sure. We almost never cite stuff in the abstract, do we?}
  % \bcp{Some people say not to, but I think their argument is weak: I've
  %   added Nick/Andre above.  But I'm not sure we want to get into stkTokens
  %   in the abstract.}
  % \fi
\end{abstract}

@@

%% Keywords
%% comma separated list
\ifcameraready
\keywords{Stack Safety, Micro-Policies}  %% \keywords are mandatory in final camera-ready submission
\fi
